---
title: "A Title About Data Science"
author: "James Poslusny"
format: html
editor: visual
editor_options: 
  chunk_output_type: inline
---

## Answering Questions

A data scientists is a person who analyzes data with the goal of:

-   Understanding trends

-   Understanding effects of variables on points of interest

-   Describing data and its impact on the world, and inversely, the impact of the world on data

-   Drawing conclusions and crafting recommendations

A data scientist and a statistician can have overlapping responsibilities, however, a statistician is expected to have a greater understanding of the mechanics of statistics and data science as a whole, as well as being able to design and implement experiments and surveys.

I personally see myself as more of a statistician at the Institute for Transportation Research and Education than a data scientist, as I will routinely encounter scenarios that are not easily described by fundamental statistical distributions, and thus require some greater understanding of both the data and statistics to deal with appropriately.

## Object "y"

Y is from the built in Iris data set. It is calculated by calling the density function on the Sepal Length variable.

```{r}
y<- density(iris$Sepal.Length)
summary(y)
```

The result is a list of 7 variables, each of which could be called on their own. The idea is that R has created an object containing all the necessary information to plot the density of the sepal length. We can now pass y to the plot function.

```{r}
#| echo: false
plot(y)
```

This is a effective and quick way of visualizing the distribution of the sepal length, although this graph would need some work before being report ready.
